Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-05-31 Manuscript.Rmd
slightly updated result

  Stability was defined as the maintenance of similar acceptance rates throughout the experimental session. The scatterplot in Fig. 4 (bottom-left and bottom-right) shows the overall proportion accepted by each participant before and after the midpoint of the session. Paired permutations showed no change in acceptance rates for the Wait and Easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the Physical group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the Cognitive group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`). Fig. 5 (left) shows that the reduction in acceptance rates in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009]. We then replicated the mixed-effects logistic regression from the previous section separately for each half of the session, which confirmed that differences among demands were stable (Fig. 5, right). Together, the consistency and stability of behavior suggested that decision makers had a clear representation of the environment.

@@

```{r Prepost mixed effects plot (Fig. 5), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1. A: Offer acceptance rates per handling time, reward amount, cost type, and session half, showing that effortful demands (Cognitive and Physical) were less frequently accepted over time, especially for the longest handling time (14 s). B: Mixed-effects logistic regression model coefficients denoting the comparison of acceptance rates across cost conditions for each half of the experimental session separately (mirrored along the diagonal). Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were preserved."}
# plots in 16.3.2
# ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
include_graphics("./Images/FIG5_prepostbtw.png")

@@

```{r Earnings/prop completed/ME plots (Fig. 6), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subject acceptance behavior. A: Quadratic relationship between trial completions and total earnings. B: Proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among cost conditions (while controlling for reward amount). Cognitive and Physical trials were compared to one another and were each compared to Wait trials from the same block (Wait-C and Wait-P, respectively). We omitted comparisons to Wait trials in the opposite block type (gray cells), which have little interpretability and were not addressed in our predictions. Asterisks mark statistically significant comparisons. D: AIC and BIC values for models of increasing complexity (AllMain refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
#ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
include_graphics("./Images/FIG6_wthlogistic.png")
```

@@

```{r New mixed effects plots (Fig. 3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time. A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM). Grey points indicate the reward-maximizing acceptance rate for each combination, which was always either 0 or 1. B: Matrix of coefficients that resulted from switching the reference cost condition in a mixed-effects logistic regression model. Each element represents how much more likely a group was to accept offers compared to the reference condition (row). White asterisks denote the p-value for significant comparisons (one, two, and three askterisks correspond to p-values under 0.05, 0.01, and 0.001, respectively). C: AIC and BIC values for a mixed-effects model comparison, ranging from a baseline intercept-only model to a full-interaction model. Both metrics yielded similar values across models."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG3_btwlogistic.png")
```

>>>>

  Stability was defined as the maintenance of similar acceptance rates throughout the experimental session. The scatterplot in Fig. 4 (bottom-left and bottom-right) shows the overall proportion accepted by each participant before and after the midpoint of the session. Paired permutations showed no change in acceptance rates for the Wait and Easy groups (*p* > 0.05), but we found significantly lower acceptance rates in the second half of the session for the Physical group (*p* `r report_p(prepost_btw$Perms[1])`, Cohen's D = `r round(prepost_btw$CohenD[1], digits = 2)`) and the Cognitive group (*p* `r report_p(prepost_btw$Perms[2])`, Cohen's D = `r round(prepost_btw$CohenD[2], digits = 2)`). Fig. 5A shows that the reduction in acceptance rates in effort groups over time was steeper for longer handling times, a hallmark of effortful demands [@Treadway2009]. We then replicated the mixed-effects logistic regression from the previous section separately for each half of the session, which confirmed that differences among demands were mostly stable (Fig. 5B; a significant difference between Physical and Easy groups during the second half of the session was due to the decrease in acceptance rates by the Physical group). Together, the consistency and stability of behavior suggested that decision makers had a clear representation of the environment.

@@

```{r Prepost mixed effects plot (Fig. 5), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1. A: Offer acceptance rates per handling time, reward amount, cost type, and session half, showing that effortful demands (Cognitive and Physical) were less frequently accepted over time, especially for the longest handling time (14 s). B: Mixed-effects logistic regression model coefficients denoting the comparison of acceptance rates across cost conditions for each half of the experimental session separately (mirrored along the diagonal). Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were mostly preserved."}
# plots in 16.3.2
# ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
include_graphics("./Images/FIG5_prepostbtw.png")

@@

```{r Earnings/prop completed/ME plots (Fig. 6), eval = !figsEnd, fig.width = 7, fig.height = 6, fig.align = "center", fig.cap = "Within-subject acceptance behavior. A: Quadratic relationship between trial completions and total earnings. B: Proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among cost conditions (while controlling for reward amount). Cognitive and Physical trials were compared to one another and were each compared to Wait trials from the same block (Wait-C and Wait-P, respectively). We omitted comparisons to Wait trials in the opposite block type (gray cells), which have little interpretability and were not addressed in our predictions. Asterisks mark statistically significant comparisons. D: AIC and BIC values for models of increasing complexity (AllMain refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
#ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
include_graphics("./Images/FIG6_wthlogistic.png")
```

@@

```{r New mixed effects plots (Fig. 3), eval = figsEnd, out.width = "70%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time. A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM). Grey points indicate the reward-maximizing acceptance rate for each combination, which was always either 0 or 1. B: Matrix of coefficients that resulted from switching the reference cost condition in a mixed-effects logistic regression model. Each element represents how much more likely a group was to accept offers compared to the reference condition (row). White asterisks denote the p-value for significant comparisons (one, two, and three askterisks correspond to p-values under 0.05, 0.01, and 0.001, respectively). C: AIC and BIC values for a mixed-effects model comparison, ranging from a baseline intercept-only model to a full-interaction model. Both metrics yielded similar values across models."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG3_btwlogistic.png")
```
